ExpressionView - an interactive viewer for biclusters identified in gene expression data

### 2010-01-14 expressionviewnote/expressionview.tex
Even more ExpressionView paper updates.

\bibitem[Ashburner et~al.(2000)]{ashburner00}
Ashburner,M. \emph{et al.} (2000)
Gene Ontology: tool for the unification of biology.
\href{http://dx.doi.org/10.1038/75556}{\emph{Nature Genetics}, {\bf 25}, 25--29.}

\bibitem[Bergmann et~al.(2003)]{bergmann03}
Bergmann,S., Ihmels,J. and Barkai,N. (2003)
Iterative signature algorithm for the analysis of large-scale gene expression data.
\href{http://dx.doi.org/10.1103/PhysRevE.67.031902 }{\emph{Physical Review E}, {\bf 67}, 031902.}

@@

\bibitem[Gentleman et~al.(2004)]{gentleman04}
Gentleman,R.C., \emph{et al.} (2004)
Bioconductor: open software development for computational biology and bioinformatics.
\href{http://dx.doi.org/10.1186/gb-2004-5-10-r80}{\emph{Genome Biology}, {\bf 5}, R80.}

\bibitem[Grothaus et~al.(2006)]{grothaus06}
Grothaus,G., Mufti,A., and Murali,TM. (2006)
Automatic layout and visualization of biclusters.
\href{http://dx.doi.org/10.1186/1748-7188-1-15}{\emph{Algorithms for Molecular Biology}, {\bf 1}, 15.}

\bibitem[Kaiser and Leisch(2008)]{kaiser08}
Kaiser,S. and Leisch,F. (2008)
A toolbox for bicluster analysis in R.
\href{http://epub.ub.uni-muenchen.de/3293/}{Technical Report 028, Department of Statistics, University of Munich}.

\bibitem[Kanehisa et~al.(2004)]{kanehisa04}
Kanehisa,M. \emph{et al.} (2004)
The KEGG resource for deciphering the genome.
\href{http://dx.doi.org/10.1093/nar/gkh063}{\emph{Nucleic Acids Res.}, {\bf 32} (Database special issue), D277.}

\bibitem[Madeira and Oliveira(2004)]{madeira04}
Madeira,S.C. and Oliveira,A.L. (2004)
Biclustering algorithms for biological data analysis: A survey.
\href{http://dx.doi.org/10.1109/TCBB.2004.2}{\emph{IEEE/ACM Transactions on Computational Biology and Bioinformatics}, {\bf 1}, 24--45.}

\bibitem[Prelic et~al.(2006)]{prelic06}
Prelic,A., \emph{et~al.} 
A systematic comparison and evaluation of biclustering methods for gene expression data 
\href{http://dx.doi.org/10.1093/bioinformatics/bt1060}{\emph{Bioinformatics}, {\bf 22}(9), 1122--1129.}

\bibitem[Santamar\'ia et~al.(2008)]{santamaria08}
Santamar\'ia,R., Ther\'on,R. and Quintales,L. (2008)
BicOverlapper: A tool for bicluster visualization. 
\href{http://dx.doi.org/10.1093/bioinformatics/btn076}{\emph{Bioinformatics}, {\bf 24}, 1212--1213.}

>>>>

\bibitem[Ashburner et~al.(2000)]{ashburner00}
Ashburner,~M. \emph{et al.} (2000)
Gene Ontology: tool for the unification of biology.
\href{http://dx.doi.org/10.1038/75556}{\emph{Nature Genetics}, {\bf 25}, 25--29.}

\bibitem[Bergmann et~al.(2003)]{bergmann03}
Bergmann,~S., Ihmels,~J. and Barkai,~N. (2003)
Iterative signature algorithm for the analysis of large-scale gene expression data.
\href{http://dx.doi.org/10.1103/PhysRevE.67.031902 }{\emph{Physical Review E}, {\bf 67}, 031902.}

@@

\bibitem[Gentleman et~al.(2004)]{gentleman04}
Gentleman,~R.C., \emph{et al.} (2004)
Bioconductor: open software development for computational biology and bioinformatics.
\href{http://dx.doi.org/10.1186/gb-2004-5-10-r80}{\emph{Genome Biology}, {\bf 5}, R80.}

\bibitem[Grothaus et~al.(2006)]{grothaus06}
Grothaus,~G., Mufti,~A., and Murali,~TM. (2006)
Automatic layout and visualization of biclusters.
\href{http://dx.doi.org/10.1186/1748-7188-1-15}{\emph{Algorithms for Molecular Biology}, {\bf 1}, 15.}

\bibitem[Kaiser and Leisch(2008)]{kaiser08}
Kaiser,~S. and Leisch,~F. (2008)
A toolbox for bicluster analysis in R.
\href{http://epub.ub.uni-muenchen.de/3293/}{Technical Report 028, Department of Statistics, University of Munich}.

\bibitem[Kanehisa et~al.(2004)]{kanehisa04}
Kanehisa,~M. \emph{et al.} (2004)
The KEGG resource for deciphering the genome.
\href{http://dx.doi.org/10.1093/nar/gkh063}{\emph{Nucleic Acids Res.}, {\bf 32} (Database special issue), D277.}

\bibitem[Madeira and Oliveira(2004)]{madeira04}
Madeira,~S.C. and Oliveira,~A.L. (2004)
Biclustering algorithms for biological data analysis: A survey.
\href{http://dx.doi.org/10.1109/TCBB.2004.2}{\emph{IEEE/ACM Transactions on Computational Biology and Bioinformatics}, {\bf 1}, 24--45.}

\bibitem[Prelic et~al.(2006)]{prelic06}
Prelic,~A., \emph{et~al.} 
A systematic comparison and evaluation of biclustering methods for gene expression data 
\href{http://dx.doi.org/10.1093/bioinformatics/bt1060}{\emph{Bioinformatics}, {\bf 22}(9), 1122--1129.}

\bibitem[Santamar\'ia et~al.(2008)]{santamaria08}
Santamar\'ia,~R., Ther\'on,~R. and Quintales,~L. (2008)
BicOverlapper: A tool for bicluster visualization. 
\href{http://dx.doi.org/10.1093/bioinformatics/btn076}{\emph{Bioinformatics}, {\bf 24}, 1212--1213.}
